---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OneNet

<!-- badges: start -->
<!-- badges: end -->

OneNet is a stability based network inference aggregation method from whole metagenome sequencing data, which aims at fostering reproducibility and precision.

## Installation

You can install the latest version of OneNet from the with the following command :

```{r install, eval=FALSE}
remotes::install_github(repo = "metagenopolis/OneNet@*release")
```

## Tutorial

A tutorial on the liver cirrhosis dataset from [Qin et. al 2014](https://pubmed.ncbi.nlm.nih.gov/25079328/) is available.
You need to build package vignettes.
```{r, eval=FALSE}
remotes::install_github(repo = "metagenopolis/OneNet@*release", build_vignettes = TRUE, force=TRUE)
library(OneNet)
vignette(package='OneNet', "Demo_offline")
```

## Citation
If you find OneNet useful, please cite:

Champion C, Momal R, Le Chatelier E, Sola M, Mariadassou M, Berland M (2024) OneNet—One network to rule them all: Consensus network inference from microbiome data. PLoS Comput Biol 20(12): e1012627. https://doi.org/10.1371/journal.pcbi.1012627
