---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OneNet

<!-- badges: start -->
<!-- badges: end -->

OneNet is a stability based network inference aggregation method from whole metagenome sequencing data, which aims at fostering reproducibility and precision.

License: MIT + file LICENSE

## Installation

You can install OneNet from the [forgemia gitlab](metagenopolis/OneNet) with:

```{r install, eval=FALSE}
remotes::install_github(repo = "metagenopolis/OneNet")
```

## Liver data set

This package includes a data set "liver", which contains 

- Abundances (semi-discrete) and metadata for a trial on healthy and liver cirrhosis patients from  [Qin et. al 2014](https://pubmed.ncbi.nlm.nih.gov/25079328/).
- A taxonomy table.
- Network inferences with 6 methods for a minimal species prevalence of 90% and 50%.

```{r}
library(OneNet)
## basic example code
data("liver")
str(liver, max.level=1)
```
